---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summstats

<!-- badges: start -->
<!-- badges: end -->

The goal of summstats is to provide useful functions for calculating summary statistics and performing data analysis tasks.

## Installation

You can install the development version of summstats from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zaralipour/summstats", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(summstats)
library(datateachr)

# Load example data
data(cancer_sample)

# Calculate summary statistics for radius_mean
calculate_summary_stats(cancer_sample, "radius_mean")
```

```{r example2}
# Calculate summary statistics grouped by diagnosis
calculate_summary_stats(cancer_sample, "radius_mean", group_by = "diagnosis")
```

## Functions

- `calculate_summary_stats()`: Calculate summary statistics (mean, median, sd, min, max, n) for numeric variables, optionally grouped by a categorical variable.

